Investigating the Effect of Dataset Representivity for Image Colourisation

### 2019-10-09 Paper/paper.tex
Added training curve and added text?

\textbf{Where get european images from?????}

\textbf{and must we show that the datasets are fundamentally different - maybe something that can be said about the source??}

@@

\begin{itemize}
	\item South Africa
	\item Soweto
	\item \textbf{etc. etc.}
\end{itemize}

A Python script was used to assimilate the International and South African images into the required ratios (of 0\% to 40\% South African image inclusion) by selecting the first \emph{n} and \emph{m} images from the image collections, respectively.

@@

For the sake of simplicity, validation and test sets have been merged into one. For each dataset, there are 40000 images in the training set and 1000 in the test/validation split. This makes it an average sized data set which means that inclusions rates on it shoud reflect to others with only minor deviation.

We found that the loss dropped immediately to a reasonable value within the first five epochs but the images produces were not of a high quality. The training process was long and slow with very little change in loss from one epoch to the next but the end results make it worthwhile.

@@

After evalutating each model on the same dataset, these are their respective losses,

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Local inclusion \% & 10\% & 20\% & 30\% & 40\% \\ 
\hline 
Loss & 0.0027 & 0.0027 & 0.0027 & 0.0027 \\ 
\hline 
\end{tabular} 
\end{table}

>>>>

Our original dataset is a subset of the Places365 dataset. This dataset consists of images that are mainly of European or Western origin. This means that if we train a model on such a dataset and then prodceed to evaluate it on South African or local images, we expect an increase in our loss. This drop in performance can be attributed to the difference in colour of local images. For example, South African landscapes have a distinct hue that is not present in European countries. South African people also have a different appearance to western people who will likely be present in European datasets.

@@

\begin{itemize}
	\item South Africa
	\item Soweto
	\item Johannesburg
	\item Kruger Park
	\item etc.
\end{itemize}

A Python script was used to assimilate the International and South African images into the required ratios (of 0\% to 40\% South African image inclusion) by randomly sampling $x$\% of images from the South African training split and $x$\% of images from the South African validation/testing split. The same number of images ($x$\%) was removed from the foreign dataset meaning that for each dataset, it contains $x$\% local data and ($100 - x$)\% foreign data where $x\in\{0, 10, 20, 30, 40\}$

@@

For the sake of simplicity, validation and test sets have been merged into one. For each dataset, there are 40000 images in the training set and 1000 in the test/validation split. This makes it an average sized data set which means that the inclusion rates on these datasets shoud reflect to other datasets of similar size with only minor deviation.

\begin{figure}[h!]
\centering
\includegraphics[width=9cm]{Curves/loss_train}
\caption{Loss curves of each dataset during training}
\label{fig:loss_train}
\end{figure}

We found that the loss dropped immediately to a reasonable value within the first five epochs but the images produces were not of a high quality. The training process was long and slow with very little change in loss from one epoch to the next but the end results make it worthwhile. Better results could have been achieved by training more models, each with a different inclusion of local data. This would allow us to draw a definative correlation of local data to loss but in this case, the samples we have taken will give us a very rough idea of the optimal parameters.

@@

After evalutating each model on the same purely South African dataset, these are their respective losses,

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Local inclusion \% & 10\% & 20\% & 30\% & 40\% \\ 
\hline 
Loss $\times 10^{-3}$& 2.638&2.638&2.638&2.638\\ 
\hline 
\end{tabular} 
\end{table}
